Output Summary

### 2023-04-27 03-post-process/output-plots-children/06-length-based-survival.Rmd

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )
}

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )
}

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )

@@

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       ylim = range(pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_lwr, phi_Pa_Mb_upr, na.rm = T),
       xlim = range(L_Pb_seq), 
       main = ifelse(i == 1, pops[j], "")
  )

@@

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )
}

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )

@@

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_lwr, phi_Mb_Ma_upr, na.rm = T),
       xlim = range(L_Mb_seq), 
       main = pops[j]
  )

>>>>

```{r phi_Pa_Mb_lim}
phi_Pa_Mb_lim = make_lim_param(post, "^phi_Pa_Mb[")
```

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Pa_Mb_lim
  )
}

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Pa_Mb_lim
  )

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Pa_Mb_lim
  )
}

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Pa_Mb_lim
  )

@@

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       # ylim = range(pred_phi_Pa_Mb_lwr, pred_phi_Pa_Mb_upr, phi_Pa_Mb_lwr, phi_Pa_Mb_upr, na.rm = T),
       ylim = phi_Pa_Mb_lim,
       xlim = range(L_Pb_seq), 
       main = pops[j]
  )

@@

```{r phi_Mb_Ma_lim}
phi_Mb_Ma_lim = sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", pop = ".", LH_type = i_spring, origin = o_nor) |>
  make_lim_param(post, param = _)
```

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)), 
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Mb_Ma_lim
  )
}

@@

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)), 
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = phi_Mb_Ma_lim
  )

@@

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       # ylim = range(pred_phi_Mb_Ma_lwr, pred_phi_Mb_Ma_upr, phi_Mb_Ma_lwr, phi_Mb_Ma_upr, na.rm = T),
       ylim = phi_Mb_Ma_lim,
       xlim = range(L_Mb_seq), 
       main = pops[j]
  )
